Data Management \\ and LSST Special Programs

### 2022-02-22 DMTN-065.tex
change read interval text

The minimum exposure time is 1 second (stretch goal: 0.1 seconds), and there is a {\it potential} hardware boundary that limits the readout rate to 1 every 15 seconds.
This {\it might} affect the image acquisition rate and increase the overheads of the proposed short-exposure micro-surveys -- but current testing of the camera system indicates that imposing waits between short exposures will not be necessary.

>>>>

The minimum exposure time is 1 second (stretch goal: 0.1 seconds), and there is a potential hardware boundary that limits the readout rate to 1 every 15 seconds.
This would affect the image acquisition rate and increase the overheads of the proposed short-exposure micro-surveys.

### 2022-02-22 ap_hardbounds.tex
change read interval text

\subsection{Inter-Image Time}
Images with exposure times $<15$ seconds {\it might} still have to be separated by $15$ seconds for thermal tolerance; i.e., the minimum readout rate might be one image every $15$ seconds, regardless of exposure time (OSS-REQ-0291; \citeds{LSE-30}).
This potential $15$ interval between images is also a potential hardware boundary on the potential diversity of data products.
Current (2022) testing of the camera system indicates that imposing waits between short exposures will not be necessary

>>>>

\subsection{Inter-Image Time}
Images with exposure times $<15$ seconds {\it might} still have to be separated by $15$ seconds for thermal tolerance; i.e., the minimum readout rate might be one image every $15$ seconds, regardless of exposure time (OSS-REQ-0291; \citeds{LSE-30}).

As discussed in Jira ticket DM-12573, the main issue is thermal and is related to the shutter, both the motors and the brakes; an elevated Camera skin temperature would affect image quality.
As of 2022, early tests suggest that a sustained (30 minutes) sequence that increases the heat load by large factors would not work, but further functional testing of the system once the Camera was fully assembled are needed for full characterization of the issue.

This potential $15$ interval between images is also a potential hardware boundary on the potential diversity of data products.
